---
title: "Panama Papers"
author: "Mark Zwart"
date: "1/13/2021"
output:
  html_document:
    css: custom-release.css
    df_print: paged
    number_sections: no
    toc: yes
    toc_float: yes
editor_options:
  chunk_output_type: inline
---

```{r Load data, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(magrittr)
library(feather)
library(stringr)
library(yaml)
library(igraph)
library(visNetwork)
if (!require("DT")) install.packages('DT')

source("load_panama_data.R")
source("plot_graph_functions.R")
invisible(
  list2env(
    load_panama_papers(read_raw_data = FALSE),
    .GlobalEnv
  ))
```


Although the title doesn't suggest it, but the data is about more than just the Panama Papers:

* [Bahamas Leaks](https://en.wikipedia.org/wiki/Bahamas_Leaks)
* [Offshore Leaks](https://en.wikipedia.org/wiki/Offshore_Leaks)
* [Panama Papers](https://en.wikipedia.org/wiki/Panama_Papers)
* [Paradise Papers](https://en.wikipedia.org/wiki/Paradise_Papers)

Data source: [https://offshoreleaks.icij.org/pages/database](https://offshoreleaks.icij.org/pages/database)


View the number of entities (Companies, officers, intermediaries addresses) per graph

```{r Show summary table of graph, echo=FALSE}
df_show <- df_graph_summaries %>% 
  filter((qty_belgian > 0 | qty_dutch > 0 | qty_uk > 0) & qty_nodes < 400) %>% 
  arrange(desc(qty_dutch + qty_belgian + qty_uk)) %>% 
  select(id_graph,
         `Source` = name_source,
         `# entities` = qty_nodes,
         `# companies` = qty_companies,
         `# officers` = qty_officers,
         `# intermediaries` = qty_intermediaries,
         `# Dutch entities` = qty_dutch,
         `# Belgian entities` = qty_belgian,
         `# UK entities` = qty_uk
         ) 
datatable(df_show)
```


Selecting the network:
```{r Selecting the network}
id_graph <- 27347	
graph_leak <- lst_graphs[[id_graph]]
txt_source <- as_data_frame(graph_leak, what = "vertices")$id_source[1]
```

The source of the selected network is the *`r txt_source`*

Create visualisation of one graph by setting the variable *id_graph*
```{r Display single network, echo=FALSE}
plot_leaks_graph(graph_leak)
```

```{r Select addresses, echo=FALSE}
df_addresses <- df_nodes %>% 
  filter(is_address == 1) %>% 
  filter(is_belgian | is_dutch | is_UK) %>% 
  select(id_node, id_source, address, countries) %>% 
  inner_join(df_edges, by = c("id_node"="to")) %>% 
  mutate(from = as.character(from)) %>% 
  inner_join(df_nodes, by = c("from"="id_node")) %>% 
  select(id_source = id_source.x,
         address = address.x,
         countries.x,
         valid_until = valid_until.x,
         incorporation_date,
         company_type,
         status,
         is_company,
         is_intermediary,
         is_officer)

write_csv2(df_addresses, "/data/panama_papers/addresses.csv")
```

